\subsection{Class diagram}
	\begin{figure}[H]
		\centering
		\begin{tikzpicture}
			%Ignore the {x,y} values while working on this, we'll change that later
			\begin{class}[text width=4cm]{User}{0,5}
			\attribute{- id : integer}
			\attribute{- name : String}
			\attribute{- password : String}
			\attribute{- emailAdress: String}
			\end{class}
		
			\begin{class}[text width=6cm]{Vote}{0,10}
			\attribute{- dateTimeSlot : DateTimeSlot }
			\operation{+ userAgreed(user: User)}
			\end{class}

			\begin{class}[text width=4cm]{DateTimeSlot}{0,14}
			\attribute{- startDate : Date}
			\attribute{- endDate : Date}
			\end{class}

			\begin{class}{Poll}{11,13}
			\attribute{- hidden : Bool}
			\attribute{- limit: Integer}
			\attribute{- closed: Bool}
			\attribute{- options: DateTimeSlot[1..*]}
			\operation{+ removeVote(vote : Vote)}
			\operation{+ addVote(vote : Vote)}
			\operation{+ changeVote(vote : Vote, changedVote: Vote)}
			\operation{+ sendNotificationEmail()}
			\operation{+ castVote(vote : Vote, user : User}
			\end{class}

			\begin{class}[text width=6cm]{Event}{11,3}
			\attribute{- id : integer}
			\attribute{- name : String}
			\attribute{- description: String}
			\attribute{- participants: User[*]}
			\attribute{- optionalMessage: String}
			\attribute{- finalDateTimeSlot: DataTimeSlot}
			\operation{+ sendInvitations()}
			\operation{+ openPoll()}
			\operation{+ closePoll()}
			\operation{+ addUser(user: User)}
			\operation{+ removeUser(user: User)}		
			\operation{+ addResponse(response: Response)}
			\operation{+ changeResponse(oldResponse : Response, newResponse: Response)}
			\operation{+ getOverview(): String}
			\operation{+ getOptions(Poll p): String}
			\operation{+ changeOption(Poll p)}
			\operation{+ getLog(): String}
			\operation{+ delete()}
			\operation{+ showPollResults()}

			\end{class}

			\begin{class}[text width=3cm]{Response}{6,9}
			\attribute{- present : Bool}
			\end{class}

			\begin{class}{dataTracker}{0,0}
			\end{class}


			%Syntax: \aggregation{ClassA}{varOfClassA}{MultofA}{ClassB}{MultofB}{varOfClassB}
			%I'm pretty sure not all are a two-way association
			\association{Response}{responses}{0..*}{User}{1}{user}
			\association{Response}{responses}{0..*}{Event}{1}{event}
			\association{DateTimeSlot}{timeslot}{1}{Vote}{1}{vote}
			\association{Vote}{castVotes}{0..*}{User}{0..*}{usersAgreed}
			\association{Vote}{votes}{0..*}{Poll}{1}{poll}
			\association{User}{organizer}{1}{Event}{organizedEvents}{0..*}
			\unidirectionalAssociation{User}{users}{0..*}{dataTracker}
			\unidirectionalAssociation{Event}{events}{0..*}{dataTracker}
			\composition{Event}{poll}{1}{Poll}
		\end{tikzpicture}
		\caption{High-level entities in the system}
		\label{fig:class-diagram}
	\end{figure}

	For most private attributes we have left out getters and setters because they are implied. For some attributes however, like the responses attribute of Event and the votes attribute of Poll, for which elements can change, we have supplied some getters, setters and changers.

	
	Classes represent real-world entities as described in section~\ref{sec:analysisdiagram}.

	
	In this model, most of the functionality is in the \emph{Event} class. We think this is quite natural since this is clearly the most important entity in the system specification.
	
	
	\emph{Note: We assume there exists a class called \textnormal{Date} that represents a date and a time.}

\subsection{Message Sequence Diagrams}
	\subsubsection{Create meeting schedule}
		\begin{figure}[H]
			\centering
			\begin{msc}{Create meeting schedule}
				\declinst{org}{User}{Organizer}
				\dummyinst{evt}
				\dummyinst{poll}
				\declinst{email}{Email}{}
				\declinst{inv}{User}{Invitee}

				\create{new}{org}{evt}{Event}{}
				\nextlevel
				\nextlevel
				\create{new}{evt}{poll}{Poll}{}
				\nextlevel

				\mess{setName()}{org}{evt}
				\nextlevel
				\mess{setDescription()}{org}{evt}
				\nextlevel
				\mess{addTimeSlot()}{org}{evt}
				\nextlevel
				\mess{addTimeSlot()}{evt}{poll}
				\nextlevel
				\mess{addTimeSlot()}{org}{evt}
				\nextlevel
				\mess{addTimeSlot()}{evt}{poll}
				\nextlevel
				\nextlevel

				\mess{addUser()}{org}{evt}
				\nextlevel
				\mess{addUser()}{org}{evt}
				\nextlevel
				\nextlevel

				\mess{setHidden()}{org}{evt}
				\nextlevel
				\mess{setHidden()}{evt}{poll}
				\nextlevel
				\nextlevel

				\mess{openPoll()}{org}{evt}
				\nextlevel
				\regionstart{coregion}{evt}
				\nextlevel
				\mess{Send confirmation}{evt}{email}
				\nextlevel
				\mess{Send confirmation}{email}{org}
				\nextlevel
				\mess{sendInvitation()}{evt}{email}
				\nextlevel
				\mess{sendInvitation()}{email}{inv}
				\nextlevel
				\regionend{evt}
				\nextlevel
			\end{msc}
			\caption{Create meeting schedule}
			\label{msc:createmeeting}
		\end{figure}

		The procedure modelled above will be executed once the User, the organizer of the Event, clicks the link indicating that he or she wants to create a new Event. 

		To do so the User organizer needs to enter a name, description and possible timeslots. These time slots will be entered into the Poll. After entering this general information the Organizer needs to add other Users to the event, to be invited. All that is left is for the organizer to choose wether to make the Poll visible to the other users. Now that all options have been set the organizer needs to open the Poll.

		After all event information has been received, messages will be sent through the Email service to all Users involved. A confirmation message will be sent to the organizer and invitations will be sent to all invited Users.

	\subsubsection{Respond to meeting invitation}
		\begin{figure}[H]
			\centering
			\begin{msc}{Respond to meeting invitation}
				\declinst{usr}{User}{Invitee}
				\dummyinst{resp}
				\declinst{evt}{Event}{}
				\declinst{poll}{Poll}{}
				\declinst{email}{Email}{}
				\declinst{org}{User}{Organizer}

				\create{new}{usr}{resp}{Response}
				\nextlevel
				\nextlevel
				\nextlevel
				\mess{setPresent()}{usr}{resp}
				\nextlevel
				\nextlevel

				\mess{addResponse(this, response)}{usr}{evt}
				\nextlevel
				\nextlevel

				\mess*{options}{poll}{evt}
				\mess*{Show DateTimeSlot options}{evt}{usr}
				\nextlevel
				\mess{Vote on options}{usr}{evt}
				\mess{Vote}{evt}{poll}
				\nextlevel
				\mess{Notification}{evt}{email}
				\mess{Send notification}{email}{org}
				\nextlevel
				\nextlevel
				
				\mess{Show stats}{evt}{usr}
				\nextlevel
			\end{msc}
			\caption{Respond to meeting invitation}
			\label{msc:respondinvite}
		\end{figure}

		This MSC models a run of the system for the usecase "Respond to meeting invitation", which describes a case where a user receives an invitation to attend an event. In our model, we assume that this can only happen via email, but one could imagine a system where already existing users receive a notification op the homepage of the website.

		The user creates a new Response, containing 'true' for his presence. This Response is added to the Event the user was invited for. The Event reads the options from its Poll and then shows them to the User. The user submits a Vote. The Event saves this in the Poll.
		It then notifies the email service which will send an email to the organizer.
		The Event will then show the statistics (number of votes for each possible DateTimeSlot) to the User.

	\subsubsection{Edit meeting response}
		\begin{figure}[H]
			\centering
			\begin{msc}{Respond to meeting invitation}
				\declinst{usr}{User}{Invitee}
				\declinst{resp}{Repsonse}{}
				\declinst{evt}{Event}{}
				\declinst{poll}{Poll}{}
				\declinst{email}{Email}{}
				\declinst{org}{User}{Organizer}

				\mess{setPresent()}{usr}{resp}
				\nextlevel
				\nextlevel

				\mess{changeResponse(this, response)}{usr}{evt}
				\nextlevel
				\nextlevel

				\mess*{options}{poll}{evt}
				\mess*{Show DateTimeSlot options}{evt}{usr}
				\nextlevel
				\mess*{previous votes}{poll}{evt}
				\mess*{Show previous votes}{evt}{usr}
				\nextlevel
				\mess{Vote on options}{usr}{evt}
				\mess{Vote}{evt}{poll}
				\nextlevel
				\mess{Notification}{evt}{email}
				\mess{Send notification}{email}{org}
				\nextlevel
				\nextlevel
				
				\mess{Show stats}{evt}{usr}
				\nextlevel
			\end{msc}
			\caption{Respond to meeting invitation}
			\label{msc:respondinvite}
		\end{figure}

		This message sequence diagram models the "Edit meeting response" use case. A user can change his present for the event. He can confirm that he is present or he can change it in a later stage when he decide he will not come to the event. When he is present he will vote when the event will be planned. If the votes are not hidden the user can see if the others are present.

		The first step is when the User sets the present attribute of the Reponse class, whether or not the user is present or not. The User can change this status at any time (if the event is not cancelled or closed in the mean time) which will cause the present status of the associated Reponse class to change. If the User is present then he or she will be presented with Vote options, represented by DateTimeStamp objects. The Event will make sure the Email service sends a notification to the organizer of the Event. The User can then see the Votes other Users cast, since this Poll is not hidden.

	\subsubsection{Administrate event}
		\begin{figure}[H]
			\centering
			\begin{msc}{Administrate event}
				\declinst{org}{User}{Organizer}
				\declinst{evt}{Event}{}

				\mess{getOverview()}{evt}{org}
				\nextlevel
				\mess{getOptions()}{evt}{org}
				\nextlevel
				\mess{changeOption(p: Poll)/delete()/getLog()}{org}{evt}
				\nextlevel
				\mess*{}{evt}{org}
			\end{msc}
			\caption{Administrate event}
			\label{msc:adminevent}
		\end{figure}

		This message sequence chart is a fairly simple one, modelling the behaviour from the "Administrate event" use case, which describes an Event administrator trying to modify a setting of an Event.

		The User first gets an overview of the Event and is then presented with all settings for the Event. The User selects one these settings and chooses the new value for this setting.

	\subsubsection{Close event}
		\begin{figure}[H]
			\centering
			\begin{msc}{Close an event}
				\declinst{org}{User}{Organizer}
				\declinst{evt}{Event}{}
				\declinst{poll}{Poll}{}
				\declinst{email}{Email}{}
				\declinst{inv}{User}{Invitee}

				\mess{Are you sure?}{evt}{org}
				\nextlevel
				\mess{Yes}{org}{evt}
				\nextlevel
				\nextlevel

				\mess{Poll results}{evt}{org}
				\nextlevel
				\mess{setFinalDateTimeSlot(d: DateTimeSlot)}{org}{evt}
				\nextlevel
				\mess{setOptionalMessage(message : String)}{org}{evt}
				\nextlevel
				\mess{Confirm email}{evt}{email}
				\nextlevel
				\mess{setClosed()}{evt}{poll}
				\regionstart{coregion}{email}
				\nextlevel
				\mess{Confirm email}{email}{inv}
				\nextlevel
				\mess{Confirm email}{email}{org}
				\nextlevel
				\regionend{email}
			\end{msc}
			\caption{Close an event}
			\label{msc:closeevent}
		\end{figure}
 
		Once a User that is the organizer of an Event decides to close that particular Event the system will first ask them for confirmation. When the User confirmes the close, the rest of the closing procedure is carried out.

		The results of the Poll will be shown to the organizer and he or she will be prompted to select the definitive date and time for the Event. The organizer can enter a custom message to be sent to all involved Users. When the organizer submits the message or indicates no specific message is needed, the Poll will be closed and Emails will be sent to all Users indicating the closing of the Poll. These Emails will contain the final date and time of the Event and the custom message if that is available.
